European or American? A re-examination of the transatlantic influence over the IMF

### 2025-05-21 manuscript/manuscript.qmd
Start describing dependent variables
formatting: remove trailing line
finish dv (short of citations)

>>>>

## Dependent Variables

In line with @lipscy2018 and @barro2005, we use the following four measures of IMF lending outcomes as our dependent variables:

-   IMF loan to GDP ratio
-   IMF participation rate
-   IMF loan to GDP approval
-   Number of IMF conditions

These variables follow the definitions used in @lipscy2018. The **loan-to-GDP ratio** captures the average size of IMF lending relative to a country's GDP over each five-year interval. The **participation rate** measures the share of months within each interval during which a country was subject to an IMF programme. The **approval indicator** is a binary variable coded 1 if a new IMF programme was initiated during the interval, and 0 otherwise. Finally, the **number of conditions** reflects the total number of performance criteria, benchmarks, and prior actions required for disbursement under IMF programmes.
